\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2015-01-28 doc/flexiblesusy-paper.tex
relax minimum required boost version to 1.41.0
adding table of contents
add little line spacings between Program Summary items

\section{Program Summary}
\noindent{\em Program title:} \fs\\ {\em Program obtainable from:}
         {\tt http://flexiblesusy.hepforge.org/}\\ {\em Distribution
           format:}\/ tar.gz\\ {\em Programming language:} {\tt
           C++, Wolfram/\mathematica, FORTRAN, Bourne shell}\\ {\em Computer:}\/ Personal computer\\ {\em Operating
           system:}\/ Tested on Linux 3.x, Mac OS X\\
         {\em External routines:}\/ SARAH 4.0.4, Boost library,
         Eigen, LAPACK\\ {\em
           Typical running time:}\/ 0.06-0.2 seconds per parameter
         point.\\ {\em Nature of problem:}\/ Determining the mass
         spectrum and mixings for any supersymmetric model. The
         generated code must find simultaneous solutions to
         constraints which are specified at two or more different
         renormalization scales, which are connected by
         renormalization group equations forming a large set of
         coupled first-order differential equations. \\ {\em Solution method:}\/
         Nested iterative algorithm and numerical minimization of the
         Higgs potential.  \\ {\em Restrictions:} The couplings must
         remain perturbative at all scales between the highest and
         lowest boundary condition.  \fs~ assumes that all couplings
         of the model are real (i.e.\ $CP-$conserving). Due to the
         modular nature of the generated code adaption and extension
         to overcome restrictions in scope is quite straightforward.

@@

\fs can be downloaded from \url{http://flexiblesusy.hepforge.org}.  To
create a custom spectrum generator the following requirements are
necessary:
%
\begin{itemize}
\item \mathematica, version 7 or higher
\item SARAH, version 4.0.4 or higher \url{http://sarah.hepforge.org}
\item C++11 compatible compiler (g++ 4.4.7 or higher, clang++ 3.1 or
  higher, icpc 12.1 or higher)
\item FORTRAN compiler (gfortran, ifort etc.)
\item Eigen library, version 3.1 or higher
  \url{http://eigen.tuxfamily.org}
\item Boost library, version 1.36.0 or higher
  \url{http://www.boost.org}
\item GNU scientific library \url{http://www.gnu.org/software/gsl}
\item an implementation of LAPACK \url{http://www.netlib.org/lapack}
  such as ATLAS \url{http://math-atlas.sourceforge.net} or
  Intel Math Kernel Library \url{http://software.intel.com/intel-mkl}
\end{itemize}
%
Optional:
%
\begin{itemize}
\item Looptools, version 2.8 or higher
  \url{http://www.feynarts.de/looptools}
\end{itemize}

>>>>

\clearpage
\section{Program Summary}
\noindent{\em Program title:} \fs\\[0.5em] {\em Program obtainable from:}
         {\tt http://flexiblesusy.hepforge.org/}\\[0.5em] {\em Distribution
           format:}\/ tar.gz\\[0.5em] {\em Programming language:} {\tt
           C++, Wolfram/\mathematica, FORTRAN, Bourne shell}\\[0.5em]
         {\em Computer:}\/ Personal computer\\[0.5em] {\em Operating
           system:}\/ Tested on Linux 3.x, Mac OS X\\[0.5em]
         {\em External routines:}\/ SARAH 4.0.4, Boost library,
         Eigen, LAPACK\\[0.5em] {\em
           Typical running time:}\/ 0.06--0.2 seconds per parameter
         point\\[0.5em] {\em Nature of problem:}\/ Determining the mass
         spectrum and mixings for any supersymmetric model. The
         generated code must find simultaneous solutions to
         constraints which are specified at two or more different
         renormalization scales, which are connected by
         renormalization group equations forming a large set of
         coupled first-order differential equations. \\[0.5em] {\em Solution method:}\/
         Nested iterative algorithm and numerical minimization of the
         Higgs potential.  \\[0.5em] {\em Restrictions:} The couplings must
         remain perturbative at all scales between the highest and
         lowest boundary condition.  \fs~ assumes that all couplings
         of the model are real (i.e.\ $CP$-conserving). Due to the
         modular nature of the generated code adaption and extension
         to overcome restrictions in scope is quite straightforward.

\clearpage
\tableofcontents

@@

\fs can be downloaded from \url{http://flexiblesusy.hepforge.org}.  To
create a custom spectrum generator the following requirements are
necessary:
%
\begin{itemize}
\item \mathematica, version 7 or higher
\item SARAH, version 4.0.4 or higher \url{http://sarah.hepforge.org}
\item C++11 compatible compiler (g++ 4.4.7 or higher, clang++ 3.1 or
  higher, icpc 12.1 or higher)
\item FORTRAN compiler (gfortran, ifort etc.)
\item Eigen library, version 3.1 or higher
  \url{http://eigen.tuxfamily.org}
\item Boost library, version 1.37.0 or higher
  \url{http://www.boost.org}
\item GNU scientific library \url{http://www.gnu.org/software/gsl}
\item an implementation of LAPACK \url{http://www.netlib.org/lapack}
  such as ATLAS \url{http://math-atlas.sourceforge.net} or
  Intel Math Kernel Library \url{http://software.intel.com/intel-mkl}
\end{itemize}
%
Optional:
%
\begin{itemize}
\item Looptools, version 2.8 or higher
  \url{http://www.feynarts.de/looptools}
\end{itemize}
